---
output: html_document
---

## Create a tree programmatically

Tree structure: 

* level 1/root: useR! 2015 Sessions
* level 2: session (name, start, end)
* level 3: room (name, seats)
* level 4: presentation (speaker, presentation name)

```{r}

library(data.tree)


useR <- Node$new("UseR! Conference 2015")
  session1 <- useR$AddChild("Session 1")
    aalborghallen <- session1$AddChild("Aalborghallen")
    aalborghallen$seats <- 790
      p1 <- aalborghallen$AddChild("Federico Marini")
      p2 <- aalborghallen$AddChild("Jonathan Clayden")
      #... etc.
    gaestsalen <- session1$AddChild("Gaestsalen")
    gaestsalen$seats <- 149
      p1 <- gaestsalen$AddChild("Costas Varsos")
      #... etc.
```

Normally, you would do this in an algorithm.

See:
```{r eval = FALSE}
vignette("ID3")
```

## OO-Style method calling

```{r eval=FALSE}
useR$ToList()
```

But you can still use "classical" R generics if you prefer. The following is equivalent:
```{r eval = FALSE}
as.list(useR)
```

## Reference Semantics
  
Nodes exhibit reference semantics:
  
```{r}
session1$day <- "Wed"
useR$Find("Session 1")$day
```

Equivalent operation with lists doesn't work:

```{r}
useRlist <- list()
  session1list <- list()
  useRlist$session1 <- session1list
  session1list$day <- "Wed"
useRlist$session1$day
```
